Lineal regression with one variable and one parameter for the cost function

### 2016-06-26 LinearRegression/Documentation/OneParam/OneParam.tex
adding gradient decend explanation for lineal regression with one varible

@@

@@

@@

@@

@@

    \begin{equation}
        \theta := \theta - \alpha
            \Bigg(
                \frac{1}{2m} \sum_{i=1}^{m}
                    \Big[
                        2 (\theta x_i - y_i) x_i
                    \Big]
            \Bigg)
    \end{equation}

@@

>>>>

    The objective of this function is to actualize the parameter $\theta$
    of the cost function J minimizing the error in each iteration, this
    is done by searching the path to the global minimum. The function
    that we are going to use is described bellow.\\

    The first thing to do is replace the function $J(\theta)$

@@

    Now the factor of the denominator has no influence on the function so it
    can be tranlated outside of the derivative

@@

    The derivative of the summatory is equal to the derivative of each term and
    then add each result, so we can insert the dirivative into the summary

@@

    Then we calculate the derivative, notice that because of derivative
    properties we must calculate the outside derivative multiplied by the inside
    derivative

@@

    Now we calculate the inside derivative

@@

    Now we can take the factor 2 outside the summatory

@@

    Finally we can see the reason why the denominator has a extra factor
    (the 2 that we added at the begining), this is with the objective
    to cancel the 2 in the numerator that result of the derivative. Finaly
    this is the resulting function that we are going to use to minimize the
    error of the algorithm
